Estimating Life-Stage Specific Habitat Capacity for Anadromous Salmonids using Quantile Random Forest Models

### 2020-01-27 analysis/paper/paper.Rmd
improved several tables.

```{r fh-samp-table}
qrf_data %>%
  # filter(Year <= 2014) %>%
  tabyl(Watershed) %>%
  adorn_totals() %>%
  adorn_pct_formatting() %>%
  # select(-percent) %>%
  kable(caption = 'The number of unique sites in the initial dataset, by watershed, with paired fish-habitat data used to populate the spring/summer Chinook salmon parr capacity model')
```

@@

```{r gaa-table}
```

```{r extrap-r2-table}
mod_fit_df = model_svy_df %>%
  select(response, data) %>%
  unnest(cols = data) %>%
  select(response, obs = qrf_cap) %>%
  group_by(response) %>%
  mutate(id = 1:n()) %>%
  left_join(model_svy_df %>%
              mutate(pred_full = map(mod_full,
                                     .f = function(x) {
                                       predict(x,
                                               type = 'response') %>%
                                         as_tibble() %>%
                                         rename(pred_full = response,
                                                pred_full_se = SE)
                                     }),
                     pred_no_champ = map(mod_no_champ,
                                         .f = function(x) {
                                           predict(x,
                                                   type = 'response') %>%
                                             as_tibble() %>%
                                             rename(pred_no_champ = response,
                                                    pred_no_champ_se = SE)
                                         })) %>%
              select(response, starts_with("pred")) %>%
              unnest(cols = starts_with("pred")) %>%
              group_by(response) %>%
              mutate(id = 1:n())) %>%
  ungroup()

@@

mod_fit_tab = mod_fit_df %>%
  group_by(response) %>%
  nest() %>%
  mutate(comp_full = map(data,
                         .f = function(x) {
                           lm(pred_full ~ obs,
                              data = x)
                         }),
         comp_no_champ = map(data,
                             .f = function(x) {
                               lm(pred_no_champ ~ obs,
                                  data = x)
                             })) %>%
  mutate(r2_full = map_dbl(comp_full,
                      .f = function(x) summary(x)$r.squared),
         r2_adj_full = map_dbl(comp_full,
                           .f = function(x) summary(x)$adj.r.squared),
         r2_no_champ = map_dbl(comp_no_champ,
                           .f = function(x) summary(x)$r.squared),
         r2_adj_no_champ = map_dbl(comp_no_champ,
                               .f = function(x) summary(x)$adj.r.squared)) %>%
  ungroup() %>%
  select(response, starts_with("r2")) %>%
  gather(type, r2, -response) %>%
  mutate(model = if_else(grepl('no_champ', type),
                         'non-CHaMP',
                         'CHaMP'),
         type = if_else(grepl('adj', type),
                        'Adjusted R2',
                        'R2')) %>%
  spread(type, r2) %>%
  mutate(response = recode(response,
                           'chnk_per_m' = 'fish/m',
                           'chnk_per_m2' = 'fish/m$^2$')) %>%
  select(Model = model,
         Response = response,
         R2, `Adjusted R2`)

@@

>>>>

```{r fh-samp-table}
qrf_data %>%
  # filter(Year <= 2014) %>%
  tabyl(Watershed) %>%
  adorn_totals() %>%
  adorn_pct_formatting() %>%
  # select(-percent) %>%
  rename(`n Sites` = n,
         Percent = percent) %>%
  kable(caption = 'The number of unique sites in the initial dataset, by watershed, with paired fish-habitat data used to populate the spring/summer Chinook salmon parr capacity model')
```

@@

```{r gaa-table}
tibble(Covariate = gaa_covars) %>%
  mutate(Scale = if_else(Covariate %in% c('NatPrin1', 
                                          'DistPrin1'),
                         'Watershed (HUC12)',
                         if_else(Covariate %in% c('WIDE_BF',
                                                  'Channel_Type',
                                                  'Elev_M'),
                                 'Site (300 m)',
                                 'Reach (2 km)'))) %>%
  kable(caption = "Globally available attribute (GAA) habitat covariates used to extrapolate quantile regression forest (QRF) model predictions of spring/summer Chinook parr capacity to a larger scale (e.g., watershed, population).")
```

```{r, eval=F}
mod_fit_df = model_svy_df %>%
  select(response, data) %>%
  unnest(cols = data) %>%
  select(response, obs = qrf_cap) %>%
  group_by(response) %>%
  mutate(id = 1:n()) %>%
  left_join(model_svy_df %>%
              mutate(pred_full = map(mod_full,
                                     .f = function(x) {
                                       predict(x,
                                               type = 'response') %>%
                                         as_tibble() %>%
                                         rename(pred_full = response,
                                                pred_full_se = SE)
                                     }),
                     pred_no_champ = map(mod_no_champ,
                                         .f = function(x) {
                                           predict(x,
                                                   type = 'response') %>%
                                             as_tibble() %>%
                                             rename(pred_no_champ = response,
                                                    pred_no_champ_se = SE)
                                         })) %>%
              select(response, starts_with("pred")) %>%
              unnest(cols = starts_with("pred")) %>%
              group_by(response) %>%
              mutate(id = 1:n())) %>%
  ungroup()

@@

mod_fit_tab = mod_fit_df %>%
  group_by(response) %>%
  nest() %>%
  mutate(comp_full = map(data,
                         .f = function(x) {
                           lm(pred_full ~ obs - 1,
                              data = x)
                         }),
         comp_no_champ = map(data,
                             .f = function(x) {
                               lm(pred_no_champ ~ obs - 1,
                                  data = x)
                             })) %>%
  mutate(r2_full = map_dbl(comp_full,
                      .f = function(x) summary(x)$r.squared),
         r2_adj_full = map_dbl(comp_full,
                           .f = function(x) summary(x)$adj.r.squared),
         r2_no_champ = map_dbl(comp_no_champ,
                           .f = function(x) summary(x)$r.squared),
         r2_adj_no_champ = map_dbl(comp_no_champ,
                               .f = function(x) summary(x)$adj.r.squared)) %>%
  ungroup() %>%
  select(response, starts_with("r2")) %>%
  gather(type, r2, -response) %>%
  mutate(model = if_else(grepl('no_champ', type),
                         'non-CHaMP',
                         'CHaMP'),
         type = if_else(grepl('adj', type),
                        'Adjusted R2',
                        'R2')) %>%
  spread(type, r2) %>%
  mutate(response = recode(response,
                           'chnk_per_m' = 'fish/m',
                           'chnk_per_m2' = 'fish/m$^2$')) %>%
  select(Model = model,
         Response = response,
         R2, `Adjusted R2`)

@@

```{r extrap-r2-table}
model_svy_df %>%
  ungroup() %>%
  mutate(n_full = map_dbl(data,
                          .f = nrow),
         k_full = map_dbl(mod_full,
                          .f = function(x) {
                            names(x$coefficients)[!grepl('Intercept', names(x$coefficients))] %>%
                              length
                          }),
         r_full = map_dbl(mod_full,
                          .f = function(x) {
                            cor(x$y, x$fitted.values)
                          }),
         r2_full = r_full^2,
         r2_adj_full = 1 - ( ( (1 - r2_full) * (n_full - 1) ) / (n_full - k_full - 1) )) %>%
  mutate(n_no_champ = map_dbl(data,
                              .f = nrow),
         k_no_champ = map_dbl(mod_no_champ,
                              .f = function(x) {
                                names(x$coefficients)[!grepl('Intercept', names(x$coefficients))] %>%
                                  length
                              }),
         r_no_champ = map_dbl(mod_no_champ,
                              .f = function(x) {
                                cor(x$y, x$fitted.values)
                              }),
         r2_no_champ = r_no_champ^2,
         r2_adj_no_champ = 1 - ( ( (1 - r2_no_champ) * (n_no_champ - 1) ) / (n_no_champ - k_no_champ - 1) )) %>%
  select(response, starts_with("r2")) %>%
  gather(type, r2, -response) %>%
  mutate(model = if_else(grepl('no_champ', type),
                         'non-CHaMP',
                         'CHaMP'),
         type = if_else(grepl('adj', type),
                        'Adjusted R2',
                        'R2')) %>%
  spread(type, r2) %>%
  mutate(response = recode(response,
                           'chnk_per_m' = 'fish/m',
                           'chnk_per_m2' = 'fish/m$^2$')) %>%
  select(Model = model,
         Response = response,
         `$r^2$` = R2, 
         `Adjusted $r^2$` = `Adjusted R2`) %>%
  kable(caption = "Summary of extrapolation model fits, split by each of the responses and whether the extrapolation model used CHaMP watershed as a covariate or not.",
        escape = F,
        digits = c(NA, NA, 3, 3))
